Semantic browsing of sound databases \\ without keywords

### 2016-02-11 lafaySsf2016.tex
remove useless fig and add new XP3.fig
add new xp link

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.18]{gfx/XP3.pdf} 
\end{center}
\caption{\label{figXP3} Acoustical Display (AD)}
\end{figure}

@@

We evaluate and compare those three displays with a crowdsourcing web-based experiment \footnote{The test is available at \url{http://217.70.189.118/soundthings/speedSoundFinding}} for which we adopt a between subject approach, \textit{i.e.} a subject can only test one display. In this experiment, subjects are asked to successively retrieve 13 target sounds among the 149 of the whole dataset. The target sounds are selected such as there are at least two target sounds in each top-level class of the semantic hierarchical structure of the dataset. To reduce order effects, target sounds are randomly presented to each subject.

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.18]{gfx/xp3.png} 
\end{center}
\caption{\label{figXP3} Acoustical Display (AD)}
\end{figure}

@@

We evaluate and compare those three displays with a crowdsourcing web-based experiment \footnote{The test is available at \url{http://soundthings.org/research/speedSoundFinding}} for which we adopt a between subject approach, \textit{i.e.} a subject can only test one display. In this experiment, subjects are asked to successively retrieve 13 target sounds among the 149 of the whole dataset. The target sounds are selected such as there are at least two target sounds in each top-level class of the semantic hierarchical structure of the dataset. To reduce order effects, target sounds are randomly presented to each subject.
